\documentclass[oneside]{sapthesis}%remove "english" for a thesis written in Italian
%Bachelor's (laurea triennale) thesis : Lau 
%Master's (laurea specialistica) thesis: LaM 
%PhD's thesis: PhD 
%\usepackage[italian]{babel} %use this package for a thesis written in Italian
\usepackage[utf8]{inputenx}
\usepackage{indentfirst}
\usepackage{microtype}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
%\usepackage{chemformula}
%\usepackage{setspace}
%\usepackage{yfonts,color}
%\usepackage{siunitx}
%\usepackage{comment}
%\usepackage{multirow}
%\usepackage{varioref}
%\usepackage[bottom]{footmisc}
%\usepackage{wrapfig}
%\usepackage{float}
%\usepackage{type1cm}
\usepackage{lettrine}
\linespread{0.9}
%\usepackage{chngcntr}
\usepackage[nottoc, notlof, notlot]{tocbibind}
%\onehalfspacing
%\counterwithout{footnote}{chapter}

\usepackage{hyperref}
\usepackage{url}
\hypersetup{
                breaklinks=true,
			hyperfootnotes=false,			
			bookmarks=true,			
			colorlinks=true,
			linkcolor=black,
                        linktoc=page,
			anchorcolor=black,
			citecolor=black,
			urlcolor=black,
			pdftitle={Thesis},
			pdfauthor={Radu Ionut Barbalata},
			pdfkeywords={thesis, sapienza, roma, university}
 }
\title{Performance Evaluation of Software Architectures using Discrete Event Simulation}
\author{Radu Ionut Barbalata}
\IDnumber{2002688}
\course{Bachelor Degree in Computer Science}
\courseorganizer{Faculty of Information Engineering, Computer Science and Statistics}
\submitdate{2024/2025}
\copyyear{2024}
\advisor{Prof. Enrico Tronci}
\coadvisor{Prof. Toni Mancini}
\authoremail{ionu.radu02@gmail.com}
\examdate{24 Octomber 2024}
\examiner{Prof. Tronci} \examiner{Prof. Arrigoni} \examiner{Prof. Bottoni}  \examiner{Prof. Gorla}  \examiner{Prof. Maselli} \examiner{Prof. Samory}  \examiner{Prof. Salvo} 

%we refer to http://ctan.mirrorcatalogs.com/macros/latex/contrib/sapthesis/sapthesis-doc.pdf for an exhaustive description of the sapthesis documentclass.


\begin{document}

\frontmatter
\maketitle
\dedication{
    \say{The destination becomes attainable only for those who embrace the journey, traversing each step with purpose along the path.}
}
%\input{./chapters/abstract}

\tableofcontents


\mainmatter

\input{chapters/abstract}

\input{chapters/introduction}

\input{chapters/preliminars}

\input{chapters/DesignImplementation}

\input{chapters/simulation_speed-up}

\input{chapters/example_real_word}

\input{chapters/validation}

\input{chapters/conclusion}

\input{chapters/acknowledgements}

\backmatter


\phantomsection
\begin{thebibliography}{17}

\bibitem{shadowTestingMicrosoft}
Microsoft. Shadow Testing in Automated Testing. Available online: \url{https://microsoft.github.io/code-with-engineering-playbook/automated-testing/shadow-testing/}.

\bibitem{PaDSS} 
    R. M. Fujimoto, \textit{Parallel and Distributed Simulation Systems}. Wiley-Interscience, 2000.

\bibitem{pqueue}
cppreference.com contributors, 
\emph{std::priority\_queue}. 
Available: \url{https://en.cppreference.com/w/cpp/container/priority_queue}.

\bibitem{bigO}
Wikipedia contributors, "Big O notation", \textit{Wikipedia, The Free Encyclopedia}, Available at: \url{https://en.wikipedia.org/wiki/Big_O_notation}

\bibitem{umap}
cppreference.com contributors, 
\emph{std::unordered\_map}. 
Available: \url{https://en.cppreference.com/w/cpp/container/unordered_map}.

\bibitem{nprs}
Wikipedia contributors, "Non-functional requirement", \textit{Wikipedia, The Free Encyclopedia}, Available at: 
\url{https://en.wikipedia.org/wiki/Non-functional_requirement}

\bibitem{loadBalancer}
Amazon Web Services, Inc. \textit{What is Load Balancing?}. Available at: \url{https://aws.amazon.com/it/what-is/load-balancing/}.

\bibitem{markovChain}
J. D. Herniter and J. F. Magee, ``Customer Behavior as a Markov Process,'' \textit{Operations Research}, vol. 9, no. 1, pp. 105-122, Jan. - Feb., 1961.

\bibitem{stationary}
``MathWorks, ``Markov Chain Analysis and Stationary Distribution,'' [Online]. Available: \url{https://it.mathworks.com/help/symbolic/markov-chain-analysis-and-stationary-distribution.html}.

\bibitem{MediumDistributedLogging}
Vaishnavi Abirami,
\textit{Mastering Microservices Logging - Best Practices Guide},
August 29, 2024. Available: \url{https://signoz.io/blog/microservices-logging/}


\end{thebibliography}

\end{document}